---
title: "Case study"
output: html_document
date: "2024-10-08"
---

```{r setup}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
library(p8105.datasets)
library(leaflet)

data(nyc_airbnb)
```

## Brainstorm questions

* Where are max and min airbnb prices?
  * what are average prices?
  * What factors affect prices? Location? Room type? Reviews?
* Where are prices going up and down over time?
* Relationship between # reviews and average review?
* Does room type affect availability?
* What's the location of different units?
  * What areas are popular?
  * Popularity = # of units? Avg price? Stays/month?
* Are there repeat hosts?
  *If so, what does that mean?
  
## Popularity by area
```{r}
nyc_airbnb |>
  count(neighbourhood_group)

nyc_airbnb |>
  group_by(neighbourhood_group) |>
  summarize(n = n(),
            avg_price = mean(price),
            avg_reviews_month = mean(reviews_per_month, na.rm = TRUE),
            avg_num_reviews = mean(number_of_reviews, na.rm = TRUE)) 
```

## examples from class people shared
```{r}
nyc_airbnb |>
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```

```{r}
nyc_airbnb |>
  group_by(room_type) |>
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb |>
  ggplot(aes(x = number_of_reviews, y=review_scores_location)) + 
  geom_point()
```

```{r}
nyc_airbnb |>
  filter(calculated_host_listings_count > 5) |>
  distinct(host_id, host_name, calculated_host_listings_count) |>
  arrange(desc(calculated_host_listings_count))
```

```{r}
 nyc_airbnb |>
  group_by(neighbourhood_group) |>
  summarise(total_reviews = sum(number_of_reviews, na.rm = TRUE)) |>
  arrange(desc(total_reviews))
```

```{r}
nyc_airbnb |>
  group_by(neighbourhood_group, room_type) |>
  summarize(mean_price = mean(price)) |>
  pivot_wider(names_from = room_type, 
              values_from = mean_price)
```

```{r}
nyc_airbnb |>
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000) |>
  ggplot(aes(x = lat, y= long, color = price)) + 
  geom_point(alpha = 0.1)
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") |>
  group_by(neighbourhood) |>
  summarize(mean_price = mean(price)) |>
  arrange(-mean_price)
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") |>
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

Go back to the map
```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000) |>
  ggplot(aes(x = lat, y= long, color = price)) + 
  geom_point(alpha = 0.1)
```

Can make it way way better with leaflet
```{r}
pal <- colorNumeric(palette = "viridis",
                    domain = nyc_airbnb$review_scores_location)

nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000) |>
  leaflet() |>
  addTiles() |>
  addCircleMarkers(~lat, ~long,
                   color = ~pal(review_scores_location),
                   radius = 2) |>
  addProviderTiles(providers$CartoDB.Positron)
```

